Simulated Observations of Young Protoplanetary Discs

### 2013-01-22 paper.tex

In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in configuration 26 of 28 for a total time of six hours, giving a beam size of between 0.02 and 0.03 arcseconds. In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted. The simulated images were cleaned down to a 3\sigma level with \sigma given by the on-line ALMA sensitivity calculator (ref).

Sensitivities:
C17O J=$3\rightarrow2$ at 337.06GHz \sigma=0.0270$\,$mJy$\,$beam$^{-1}$
OCS J=$26\rightarrow25$ at 316.15GHz \sigma=0.0275$\,$mJy$\,$beam$^{-1}$
HCO$^+$ J=$3\rightarrow2$ at 267.56GHz \sigma=0.0176$\,$mJy$\,$beam$^{-1}$
H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz \sigma=0.0228$\,$mJy$\,$beam$^{-1}$

@@

 \caption{Integrated intesity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}$\rightarow3$_{03}$, {\bf Top Right:}C$^{17}$O 3\rightarrow2, {\bf Bottom Left:} OCS 26\rightarrow25 and {\bf Bottom Right:} HCO$^+$ 3\rightarrow2. contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5\sigma and increases in intervals of 5\sigma}
\end{figure*}

@@

 \caption{Spectra for each of the simulated species. In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=\pm N (plus blue, minus red) where N is different for each species. the values for N are: H$_2$CO 20AU, C$^{17}$O 28AU, OCS 10AU, HCO$^+$ 38AU. {\bf maybe should put stars or something on the mom0 maps to show these locations?}}
\end{figure*}

>>>>

In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in configuration 26 of 28 for a total time of six hours, giving a beam size of between 0.02 and 0.03 arcseconds. In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted. The simulated images were cleaned down to a 3$\sigma$level with $\sigma$given by the on-line ALMA sensitivity calculator (ref).

Sensitivities:
C17O J=$3\rightarrow2$ at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$
OCS J=$26\rightarrow25$ at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$
HCO$^+$ J=$3\rightarrow2$ at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$
H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$

@@

 \caption{Integrated intesity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2. contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.}
\end{figure*}

@@

 \caption{Spectra for each of the simulated species. In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is different for each species. the values for N are: H$_2$CO 20AU, C$^{17}$O 28AU, OCS 10AU, HCO$^+$ 38AU. {\bf maybe should put stars or something on the mom0 maps to show these locations?}}
\end{figure*}
